\begin{recipe}
[ %
	preparationtime = {\SI{1}{\hour}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{2}},
	source = {mithodin}
    ]{Cauliflower Gashi}

    \introduction{
    	You can replace fresh coconut with \SI{500}{\milli\liter} of coconut milk.
	}

	\ingredients[21]{
		\SI{120}{\gram} & Freshly grated coconut \\
		\SIrange{7}{8}{\tablespoon} & Oil \\
		\SI{300}{\gram} & Onion, diced\\
		5 & dried red chilis \\
		\SI{2}{\teaspoon} & Coriander seeds \\
		\SI{1/8}{\teaspoon} & Mustard seeds \\
		\SI{1/8}{\teaspoon} & Fenugreek seeds \\
		\SI{1/4}{\teaspoon} & Cumin seeds \\
		\SI{2.5}{\centi\meter} & Cinnamon bark \\
		4 & Black peppercorns \\
		2 & Cloves \\
		\SI{1/2}{\teaspoon} & Turmeric \\
		\SI{1/2}{\teaspoon} & Paprika powder \\
		1\,heaped tsp & Tamarind paste \\
		$2\times 1$\,\si{\centi\meter} & Piece of ginger, finely diced or grated \\
		\SI{4}{cloves} & Garlic, finely diced \\
		\SI{200}{\gram} & Potatoes, peeled and roughly diced \\
		& Salt \\
		\SI{400}{\gram} & Cauliflower, separated into large pieces \\
	}

	\preparation{
		\step Infuse \SI{80}{\gram} of grated coconut in \SI{500}{\milli\liter} of water for \SI{30}{\minute}.

		\step Put a clean piece of cloth into a sieve, filter out the coconut pieces and keep the fluid.

		\step Heat \SI{1}{\tablespoon} oil in a frying pan, roast the rest of the grated coconut for \SIrange{2}{3}{\minute}. Take out of the pan and put aside.

		\step Add another \SI{1}{\tablespoon} of oil and sweat off half of the onions for \SIrange{2}{3}{\minute}. Put onions aside.

		\step Add another \SI{1}{\tablespoon} of oil. Roast chilis, coriander seeds, mustard seeds, fenugreek seeds, cumin seeds, cinnamon bark, peppercorns and cloves for \SI{30}{\second}.

		\step Put roasted coconut, onions, roasted spices and tamarind paste into a food processor with \SI{125}{\milli\liter} and blend into a fine paste.

		\step Heat the rest of the oil in a saucepan, sweat off ginger and garlic for \SI{15}{\second}. Add the rest of the onions and sweat off for another \SIrange{7}{8}{\minute}.

		\step Add spice paste and sweat for another \SI{2}{\minute}.

		\vspace{1em}

		\step Add a little bit of water and the potatoes, cook for \SI{5}{\minute}.

		\vspace{1em}

		\step Add about \SI{1}{\teaspoon} of salt, add \SI{125}{\milli\liter} of water and simmer on a medium-low heat for \SIrange{6}{7}{\minute}.

		\step Add cauliflower and the coconut water you made (or coconut milk) and cook until the vegetables are soft.

		\step Serve with rice or naan bread.
	}

\end{recipe}