\begin{recipe}
[ %
	preparationtime = {\SI{1}{\hour} (\SIrange{12}{24}{\hour} to marinate)},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{3--4}},
	source = {Roosevelt}
    ]{Chicken Tikka Masala}

%    \introduction{
%
%	}

	\ingredients[15]{
		\SI{4}{\teaspoon} & Garlic \\
		\SI{4}{\teaspoon} & Ground ginger \\
		\SI{4}{\teaspoon} & Ground turmeric \\
		\SI{2}{\teaspoon} & Ground garam masala \\
		\SI{2}{\teaspoon} & Ground coriander \\
		\SI{2}{\teaspoon} & Ground cumin \\
		\SI{1}{\tablespoon} & Salt \\
		\SI{1x1/2}{\cup} & Plain, non-greek yogurt \\
		\SI{2}{\pound} & Chicken thighs, cut into pieces \\
		\SI{3}{\tablespoon} & Oil or ghee \\
		1 & Onion, chopped \\
		\SI{30}{\milli\liter} & Tomato paste \\
		\SI{1/4}{\teaspoon} & Cardamom \\
		\SI{1}{\teaspoon} & Red pepper flakes \\
		\SI{28}{\ounce} & Canned chopped tomato \\
		\SI{2}{cups} & Cream \\
		& Cilantro
	}

	\preparation{

		\textbf{Half a day, or overnight, before:}

		\step Mix together the garlic, ginger, turmeric, garam masala, coriander and cumin. Store half of the mix for later.

		\step Put the other half in a glass container with salt, yogurt and the chicken thighs. Cover and leave to marinate.

		\textbf{When ready to cook:}

		\step Cook the oil, onion, tomato paste, cardamom and red pepper flakes in a pot until blacked and stuck to the pot.

		\step Add remaining half of the spices reserved from earlier and cook a bit more until blackened.

		\step Stir in the chopped tomato to deglaze. Add the cream and simmer for \SI{30}{\minute}, stirring very often so it doesn't burn.

		\step While the sauce is simmering, cook the chicken under the broiler until blackened (about \SI{10}{\minute}) on a wire rack.

		There should be blackened parts on the chicken from the yogurt and spices.

		\step Add the chicken, along with a touch of cilantro, to the pot after it is done simmering and let the chicken finish cooking if needed.
	}

\end{recipe}