\begin{recipe}
[ %
	preparationtime = {\SI{2}{\hour}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion[Gyros]{4--5}},
	source = {chimingfish (from \href{https://www.the-girl-who-ate-everything.com/chicken-gyros-opa/}{The Girl Who Ate Everything})}
    ]{Chicken Gyros}
    
    \introduction{
    	I usually cook the chicken using my broiler. 
    	
    	If you're using a regular to particularly thick chicken breast, I recommend either butterflying it or pounding it thin with the flat side of a meat tenderizer before marinating it so that it'll cook more quickly and evenly later. 
    	
    	Finally, the tzatziki can be made further ahead of time and the chicken can be marinated for longer than an hour if desired.
	}

	\ingredients[19]{
		\multicolumn{2}{c}{\textbf{Tzatziki sauce:}} \\
		\SI{1}{\cup} & Plain Greek yogurt \\
		1 & Regular cucumber peeled and seeded \\
		\SI{1}{\teaspoon} & Minced garlic \\
		\SI{1}{\teaspoon} & White wine vinegar \\
		& Salt and pepper \\
		& Squeeze of fresh lemon juice \\
		& Extra virgin olive oil \\
 		\multicolumn{2}{c}{\textbf{For the chicken:}} \\
 		\SI{1x1/4}{\pound} & Boneless skinless chicken breasts \\
		\SI{2}{\teaspoon} & Minced garlic \\
		& Juice of 1 lemon (\SIrange{2}{3}{\tablespoon}) \\
		\SI{2}{\teaspoon} & Red wine vinegar \\
		\SI{2}{\tablespoon} & Extra virgin olive oil \\
		\SI{2}{\tablespoon} & Plain Greek yogurt \\
		\SI{1}{\tablespoon} & Dried oregano \\
		& Salt and pepper \\
		\multicolumn{2}{c}{\textbf{To assemble:}} \\
		& Pita bread \\
		& Fresh tomatoes, seeded and diced \\
		& Red onion, sliced thin \\
		& Feta cheese, crumbled
	}

	\preparation{
		
		\textbf{Tzatziki sauce}
		 
		\step Shred the cucumber or chop in food processor. Wrap in a towel and squeeze to remove as much water as possible. 
		
		\step Mix together the yogurt, shredded cucumber, garlic, white wine vinegar, salt and pepper to taste, and lemon juice. Drizzle lightly with olive oil.

		\step Refrigerate for at least \SI{30}{\minute} before serving to allow the flavors to meld.
		
		\textbf{Chicken}
		
		\step Combine the garlic, lemon juice, red wine vinegar, olive oil, yogurt, oregano, and salt and pepper to taste in a medium bowl. Whisk together until mixed well. 
		
		\step Add the chicken pieces to the bowl and mix well to coat. 
		
		\step Cover and refrigerate for about \SI{1}{\hour}.
		
		\vspace{1em}
		\pagebreak
		
		\step Cook the chicken as desired, either in the skillet or with the broiler. 
		
		\vspace{1em}
		
		\step Once the chicken is completely cooked through, transfer to a plate and let rest for \SI{5}{\minute}.
	}
    
\end{recipe}