\begin{recipe}
[ %
	preparationtime = {\SI{1x1/2}{\hour}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{6--8}},
	source = {chimingfish},
	sourceref = {\href{https://www.bonappetit.com/recipe/digaag-qumbe-yogurt-coconut-chicken}{Bonappetit}}
    ]{Digaag Qumbe}

	\pretitle{{\color{gray}\Large Yogurt-coconut chicken}\vspace{-1.5ex}}

    \introduction{
    	I've never actually tried serving over spinach, I usually just do rice. Also, I usually leave out the ghee, and I use plain Greek yogurt.
	}

	\ingredients[22]{
		3 & Medium tomatoes (about \SI{6}{cups}) \\
		1 & Red bell pepper \\
		2 & Jalape\~nos \\
		\SI{1/2}{\cup} & Extra-virgin olive oil \\
		2 & Onions \\
		2 & Large garlic cloves \\
		1 & \SI{1}{\inch} piece fresh ginger (about \SI{1}{\tablespoon}) \\
		\SI{1}{\tablespoon} & Curry powder \\
		\SI{1}{\tablespoon} & Ground cumin \\
		\SI{1}{\teaspoon} & Ground turmeric \\
		\SI{1/4}{\teaspoon} & Ground cardamom \\
		& Kosher salt \\
		\SI{1}{\cup} & Plain yogurt \\
		\SI{1}{\tablespoon} & Tomato paste \\
		1 & Yukon Gold potato\\
		1 & Carrot \\
		\SI{2}{\pound} & Skinless, boneless chicken thighs \\
		1 & \SI{14}{\ounce} can of coconut milk \\
		\SI{3}{\tablespoon} & Ghee (optional) \\
		\SI{1}{\cup} & Cilantro, plus whole leaves for serving \\
		& Steamed rice and/or spinach (for serving) \\
		& \textbf{Optional:} Bananas for serving \\
	}

	\preparation{
		\step Remove seeds and membranes from the bell pepper and, optionally\footnote{If you want less heat.}, jalape\~nos, and coarsely chop both along with tomatoes.

		\step Blend tomatoes, bell pepper, and jalapeños in a blender or food processor until almost smooth; set aside.

		\step Heat oil in a large pot over medium. Add chopped onion and finely chopped garlic and cook, stirring often, until beginning to soften; about \SI{5}{\minute}.

		\step Add peeled and finely chopped ginger, cumin, curry powder, turmeric, and cardamom; season generously with salt. Cook, stirring, until very fragrant; about \SI{1}{\minute}.

		\step Add reserved tomato mixture to pot and stir well to combine. Stir in yogurt and tomato paste, cover pot, and simmer 10 minutes.

		\step Add potato -- peeled and cut into \SI{3/4}{\inch} cubes -- and carrot -- peeled, cut into \SI{1/4}{\inch}-thick coins -- and continue to cook, stirring occasionally, until vegetables are nearly tender, \SIrange{15}{18}{\minute}.

		\step Add chicken cut into \SI{1}{\inch} pieces, coconut milk, ghee (if using), and \SI{1}{\cup} coarsely chopped cilantro. Stir to combine, then simmer until chicken is tender and sauce thickens, about \SI{20}{\minute}.

		(Make sure to simmer with an uncovered pot here to allow water to evaporate off.)

		\step Season with salt. Divide rice among bowls. Spoon chicken, vegetables, and sauce over. Top with cilantro leaves.

		\textbf{Optional:} Serve with a banana.
	}

\end{recipe}