\begin{recipe}
[ %
	preparationtime = {\SI{45}{\minute}},
	bakingtime={\SI{30}{\minute}},
	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{350}{\fahrenheit} (\SI{180}{\celsius})}},
	portion = {\portion[Brownies]{20}},
	source = {chemistring}
    ]{Espresso Brownies}

    \introduction{
    	If the amount of coffee overwhelms you, you can cut back by 2 or even 4 tablespoons of espresso powder.  The brownies will still taste terrific!

    	\textbf{Variation:} Recipe can be converted to green tea blondies by replacing espresso powder with \SIrange{2}{3}{\tablespoon} matcha (green tea) powder and using white chocolate chips.
	}

	\ingredients[]{
		\SI{3/4}{\cup}  & Butter \\
		\SI{1}{\cup} & Brown sugar, lightly packed \\
		\SI{1/2}{\cup} & Granulated (white) sugar \\
		\SI{1}{\teaspoon} & Vanilla \\
		\SI{1/4}{\teaspoon} & Salt \\
		3 & Eggs \\
		\SI{1/2}{\cup} & Instant espresso coffee powder (not dissolved) \\
		\SI{1}{\cup} & Flour \\
		\SI{3/4}{\teaspoon} & Baking powder \\
		\SI{3/4}{\cup} & Chocolate chips \\
		& Powdered sugar (optional)
	}

	\preparation{
		\step Preheat oven to \SI{350}{\fahrenheit} (\SI{180}{\celsius}). Butter a \SI{9}{\inch} square pan.

		\step In a large bowl, beat together melted butter and sugars. Add vanilla, salt, and eggs. Beat until well blended. Stir in espresso powder, flour, and baking powder, mixing until smooth. Fold in chocolate chips. Pour batter into pan.

		\step Bake about \SI{30}{\minute}, or until tooth pick inserted in center comes out clean. Cool completely in pan.

		\step Lightly dust top with powdered sugar, and cut into bars -- makes 20 brownies.
	}

\end{recipe}