\begin{recipe}
[ %
	preparationtime = {\SI{3}{\hour}},
	bakingtime={\SIrange{20}{25}{\minute}},
	bakingtemperature={\protect\bakingtemperature{
			topbottomheat=\SI{200}{\celsius} (\SI{400}{\fahrenheit}),
			fanoven=\SI{180}{\celsius} (\SI{350}{\fahrenheit}),
			gasstove=3
		}},
	portion = {\portion[Focaccia]{1}},
	source = {chemistring}
    ]{Focaccia with Olives and Rosemary}

    \introduction{
    	\textbf{Variations:} Infinite! Replace olives with sundried tomatoes. Add minced garlic, oregano, finely shredded asiago cheese, other herbs directly to the dough and omit olives and rosemary.
	}

	\ingredients[17]{
		\SI{7}{\gram} (\SI{1/2}{\tablespoon}) & Dried yeast \\
		\SI{1}{\teaspoon} & Sugar \\
		\SI{150}{\milli\liter} (\SI{1/2}{\cup}) & Water at room temperature \\
		\SI{3}{\tablespoon} & Fresh rosemary \\
		\SI{350}{\gram} (\SI{11}{\ounce}) & All purpose wheat flour \\
		\SI{1}{\teaspoon} & Salt \\
		\SI{80}{\milli\liter} (\SI{1/3}{\cup}) & Olive oil \\
		\SI{3}{\tablespoon} & Cold pressed olive oil \\
		approx.\ 15 & Black olives \\
		\SI{2}{\tablespoon} & Coarse ground sea salt \\
		& Olive oil to grease the baking tray \\
		& Flour for the work surface \\
		& Baking tray
	}

	\preparation{
		\step Dissolve yeast with the sugar in the lukewarm water.

		\step Finely chop \SI{2}{\tablespoon} of rosemary leaves.

		\vspace{1em}

		\step Sieve the flour into a large mixing bowl and make a well in the center. Add the salt, dissolved yeast, chipped rosemary, and the olive oil, and knead everything into a firm, workable dough for about \SI{5}{\minute}.

		\step Cover the bowl with a dishtowel and leave the dough to stand in a warm place at a constant temperature for about \SI{2}{\hour}.

		\step Place the dough on a lightly floured work surface and knead again. Next, roll it out to form a flat rectangle $\SI{20}{\centi\meter}\times \SI{20}{\centi\meter}$ ($\SI{8}{\inch}\times \SI{12}{\inch}$). The dough should be slightly thicker at the edges than in the middle.

		\step Preheat the oven to \SI{200}{\celsius} (\SI{400}{\fahrenheit}, fan-assisted \SI{180}{\celsius}/\SI{350}{\fahrenheit}, gas mark 3).

		\vspace{1em}

		Note: this should give about \SI{20}{\minute} to let the bread rise a second time.

		\step Grease and lightly flour the baking tray and lay the bread on it. Using the handle of a wooden spoon (or your finger), press dents into the dough at regular intervals.

		\step Brush the surface of the dough liberally with the cold pressed olive oil. Push an olive into each of the dents and sprinkle the dough with the coarse ground sea salt and the rest of the rosemary.

		\step Bake in the preheated oven for about \SIrange{20}{25}{\minute} until golden brown.

		\vspace{1em}

		\step Serve while still warm.
	}

\end{recipe}