\begin{recipe}
[ %
	preparationtime = {\SI{45}{\minute}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{6}},
	source = {chemistring}
    ]{Gouda and Lentil Soup}

    \introduction{
    	Recipe is easily modified.  Sweet potato can be replaced by butternut squash, gouda can be replaced by old cheddar or other sharp cheese, lentils can be replaced by chick peas (or bean of choice), canned tomatoes or other vegetables (peppers, carrots) can be added as desired.
	}

	\ingredients[]{
		\SI{1}{\tablespoon} & Butter \\
		\SI{1}{\cup} & Chopped onion \\
		\SI{1}{\cup} & Thinly sliced celery (or baby spinach leaves) \\
		\SI{4}{cups} & Peeled diced sweet potato \\
		\SI{1/2}{\teaspoon} & Ground cumin \\
		\SI{4}{cups} & Low sodium chicken broth \\
		\SI{19}{\ounce} (\SI{540}{\milli\liter}) & Can lentils, drained and rinsed \\
		\SI{1}{\cup} & Shredded gouda cheese, divided \\
		& Salt and pepper to taste \\
		\SI{1/2}{\cup} & Grape or cherry tomatoes, quartered
	}

	\preparation{
		\step In a pot, melt butter over medium-high heat. Add onions and celery and saut\'e for \SI{3}{\minute} or until softened.

		\step Stir in sweet potatoes and cumin, saut\'e for \SI{2}{\minute}.

		\step Add broth and bring to a boil. Reduce heat and simmer, covered, for \SIrange{8}{10}{\minute} or until potatoes are tender.

		\step In a blender (or with hand/stick blender), puree soup until smooth. Return to pot.

		\step Stir in lentils, cook on medium heat for \SI{2}{\minute} or until heated through.

		\step Remove from heat and stir in \num{1/2} of the gouda (and all of the spinach leaves, if using). Season to taste with salt and pepper.

		\step Ladle soup into bowls and sprinkle each serving with remaining gouda and tomatoes.
	}

\end{recipe}