\begin{recipe}
[ %
	preparationtime = {\SI{1x1/2}{\hour}},
	bakingtime={\SIrange{40}{45}{\minute}},
	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{180}{\celsius} (\SI{350}{\fahrenheit}),
													fanoven=\SI{160}{\celsius},
													gasstove= 4}},
	portion = {\portion{6--8}},
	source = {mithodin (from \href{https://www.youtube.com/user/FrenchGuyCooking}{Just a French Guy Cooking})}
    ]{Gratin Dauphinois}

    \introduction{
    	It's the perfect comfort food for a cold winter day.
	}

	\ingredients[10]{
		about \SI{1x1/2}{\kilo\gram} & Medium-sized firm-fleshed waxy potatoes \\
		\SI{450}{\milli\liter} & Whole milk \\
		\SI{450}{\milli\liter} & Double cream \\
		1 & Bay leaf \\
		& A pinch of freshly grated nutmeg \\
		\SI{40}{\gram} & Grated cheese (Le Gruyere is perfect for this; anything that will
		gratinate nicely) \\
	}

	\preparation{
		\step Preheat the oven to \SI{180}{\celsius} (\SI{350}{\fahrenheit}, \SI{160}{\celsius} fan, gas 4).

		\step Wash, then peel and cut the potatoes into \SI{5}{\milli\meter} thick slices. Season with black pepper and salt.

		\step Put the slices into a saucepan, add the milk, cream and bay leaf and simmer gently for about \SI{10}{\minute}.

		\step Lift out the potatoes with a slotted spoon into a bowl and set them aside. Season the milk and cream with the nutmeg and, if neccessary, salt and pepper. Discard the bay leaf.

		\step Layer the potato slices and cream mixture alternately in a greased ovenproof dish, seasoning lightly between the layers.

		\step Bake in the oven for \SIrange{40}{45}{\minute} or until the potatoes are tender when pierced with a skewer or the tip of a knife.

		\step Take the dish out of the oven and switch on the grill. Sprinkle over the grated cheese and grill until the top is golden and crusty.
	}

\end{recipe}