\begin{recipe}
[ %
	preparationtime = {\SIrange{2}{3}{\hour}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{4--6}},
	source = {chimingfish},
	sourceref = {\href{https://www.bonappetit.com/recipe/mushroom-carbonara}{Bonappetit}}
    ]{Mushroom Carbonara}

    \introduction{
		I usually up the mushrooms to \SI{2}{\pound} because I like having a higher shroom:pasta ratio. Also, I can never find orecchiette, so I usually substitute in mediumish sized shells.
	}

	\ingredients[11]{
		\SI{1x1/2}{\pound} & Crimini or button mushrooms \\
		6 clove & Garlic \\
		2 & Medium shallots \\
		\SI{1}{\cup} & Parsley leaves with tender stems (about $\sfrac{1}{2}$ bunch) \\
		5 & Large egg yolks \\
		1 & Large whole egg \\
		\SI{4}{\ounce} & Store-bought pre-grated Parmesan, plus more for serving \\
		\SI{1x1/2}{\teaspoon} & Freshly ground black pepper, plus more for serving \\
		\SI{1/2}{\cup} & Extra-virgin olive oil \\
		\SI{1}{\pound} & Orecchiette \\
		& Kosher salt
	}

	\preparation{
		\step Set a large pot of water to boil, salting the water when boiling.

		\step Meanwhile, tear off and discard the stems of the mushrooms and tear the mushrooms into halves or quarters. Lightly smash and thinly slice the garlic, finely chop the shallots, and coarsely chop the parsley.

		\step Heat another large pot over medium high heat for ~\SI{3}{\minute} (Dutch ovens work well here). Add the olive oil and mushrooms, and toss to coat. Cook, stirring every \SIrange{4}{5}{\minute} or so, until mushrooms are golden brown, ~\SIrange{13}{18}{\minute}. Note that the mushrooms will release a lot of liquid, and you want to cook at least most, if not all of it off.

		\step Meanwhile, put the egg yolks, egg, Parmesan, and pepper in a bowl and whisk together until combined. Set aside.

		\step Once the mushrooms have been cooking for ~\SI{10}{\minute}, add your pasta to the salted boiling water. Cook until ~\SI{2}{\minute} short of \textit{al dente}.

		\step After the mushrooms have finished browning, add the garlic, shallots, and \SI{1x1/2}{\teaspoon} salt to the mushrooms. Cook, stirring often, for ~\SI{1}{\minute}.

		\step Once pasta is ~\SI{2}{\minute} off \textit{al dente}, reserve ~\SI{2}{cups} of pasta water, then drain the pasta.

		\step Add the pasta and ~\SI{1}{\cup} of water to the mushrooms, and cook over medium-low heat for ~\SI{2}{\minute}, stirring often. After this, remove from heat and let cool for \SI{1}{\minute}.

		\step Add ~\SI{1/2}{\cup} of the pasta water to the egg mixture, and whisk to combine.

		\vspace{1em}

		\step Gradually add the egg mixture to the pasta, stirring vigorously, and add some more pasta water if the sauce is still too thick.

		\step Stir in the parsley, salt to taste, and serve with more Parmesan/pepper.
	}

\end{recipe}