\begin{recipe}
[ %
	preparationtime = {\SI{2}{\hour}},
%	bakingtime={\SI{1}{\hour}},
%	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{280}{\celsius}}},
	portion = {\portion{4}},
	source = {mithodin},
	sourceref = {Italien vegetarisch}
    ]{Saffron Risotto with Porcini mushrooms}

    \introduction{
    	I love this one, but you can sub basically anything for the saffron and mushrooms.

    	Dried mushrooms work as well, but it doesn't look as nice. You can also replace risotto rice with any short-grain glutinous rice.

    	You can replace the broth with pre-made bullion.
	}

	\ingredients[18]{
		\multicolumn{2}{c}{\textbf{Broth:}} \\
		1 & Carrot \\
		1 & Stalk of celery \\
		2 & Stalks of flat leaf parsley \\
		1 & Onion \\
		\SI{1}{\tablespoon} & Sea salt \\
		\multicolumn{2}{c}{\textbf{Risotto:}} \\
		\SI{400}{\gram} & Fresh Porcini mushrooms \\
		1 & Shallot \\
		\SI{50}{\gram} & Butter \\
		\SI{320}{\gram} & Risotto rice \\
		\SI{100}{\milli\liter} & White wine \\
		\SI{0.2}{\gram} & Saffron threads \\
		\SI{100}{\gram} & Parmigiano Reggiano \\
		& A little bit of flat leaf parsley \\
		\SI{1}{clove} & Garlic \\
		\SI{50}{\gram} & Cold butter \\
		\SI{2}{\tablespoon} & Extra virgin olive oil \\
		& Sea salt \\
		& Freshly ground black pepper \\
	}

	\preparation{

		\textbf{Broth:}

		\step Wash and/or peel the vegetables and parsley.

		\step Put in a pot with \SI{1.2}{\liter} of cold water and bring to a boil. Simmer for about \SI{1}{\hour}.

		\step Discard the vegetables, keep the liquid warm.

		\textbf{Risotto:}

		\step Grate the parmigiano, wash the parsley and finely chop it (including the stalks). Peel and finely dice the garlic and shallot. Clean mushrooms and slice thinly.

		\step Melt \SI{50}{\gram} of butter, soften the diced shallot for \SIrange{5}{10}{\minute} on a low heat (you don't want browning).

		\step Add the rice, bring up the temperature while stirring, until the rice looks glassy.

		\step Deglaze with white wine, let it evaporate.

		\vspace{1em}

		\step Now add the broth one ladle at at time, while stirring more or less constantly. It's very easy to burn your rice here.

		Wait for one batch of broth to be absorbed by the rice before adding the next.

		\step Soak the saffron threads in a little bit of broth and near the end of the cooking process.

		\step After about \SI{20}{\minute}, start testing if the rice is done.

		\vspace{1em}

		You're looking for a creamy texture with a slight bit of a bite left in the rice.

		\step While the risotto is absorbing the water, fry the mushroom slices with the garlic in some olive oil.

		\step Season with salt and pepper, add chopped parsley.

		\vspace{1em}

		Keep some nice slices for garnish, add the rest to the risotto near the end of the cooking process.

		\step Take the risotto off the heat, stir in cold butter and grated parmigiano. Rest for \SI{3}{\minute}.

		\step Plate up and garnish with mushrooms and some more grated parmigiano.
	}

\end{recipe}