\begin{recipe}
[ %
	preparationtime = {\SI{45}{\minute}},
	bakingtime={\SI{15}{\minute}},
	bakingtemperature={\protect\bakingtemperature{topbottomheat=\SI{350}{\fahrenheit} (\SI{180}{\celsius})}},
	portion = {\portion{4}},
	source = {chemistring}
    ]{Shrimp and Feta Casserole}

    \introduction{
    	Lazy version: use pre-cooked thawed shrimp. Add shrimp and feta cheese to sauce and simmer on stove until warmed through -- not as pretty, but just as tasty.
	}

	\ingredients[]{
		\SI{2}{\tablespoon} (\SI{30}{\milli\liter}) & Butter \\
	    1 & Medium onion, finely chopped \\
	    \SI{1/2}{bunch} & Green onions, finely chopped \\
	    \SI{1}{clove} & Garlic, minced \\
	    \SI{14}{\ounce}/\SI{398}{\milli\liter} & Diced tomatoes (\SI{1}{can}) \\
	    \SI{7.5}{\ounce}/\SI{213}{\milli\liter} & Tomato sauce (\SI{1}{can}) \\
	    \SI{1/4}{\cup} (\SI{50}{\milli\liter}) & Dry white wine \\
	    \SI{3}{\tablespoon} (\SI{45}{\milli\liter}) & Chopped parsley \\
	    \SI{1/2}{\teaspoon} (\SI{2}{\milli\liter}) & Dried oregano leaves, crushed \\
	    \SI{1.5}{\pound} (\SI{750}{\gram}) & Fresh, or frozen and thawed, large shrimp, shelled, deveined \\
	    \SI{8}{\ounce} (\SI{250}{\gram}) & Feta cheese, coarsely crumbled \\
	    & Black olives, chopped (optional)
	}

	\preparation{
		\step Melt butter in large frypan. Saut\'e onions and garlic over medium-high heat, \SI{4}{\minute} or until soft.

		\step Add tomatoes and their juice, tomato sauce, wine, parsley, and oregano. Heat to boiling.

		\step Reduce heat and simmer, uncovered, \SI{10}{\minute} or until slightly thickened. Stir occasionally.

		\step Add shrimp to sauce. Spoon into 2-quart (\SI{2}{\liter}) shallow casserole. Scatter the cheese over the top, press lightly into sauce.

		\step Bake in \SI{350}{\fahrenheit} (\SI{180}{\celsius}) oven \SI{15}{\minute} or until shrimp are pink and casserole is heated through.

		\step Garnish with chopped black olives if desired. Serve with crusty bread.
	}

\end{recipe}